---
title: "Test_09_03_2020"
author: "Yihuan Huang"
date: "9/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("function_0822.R")
library(stats)
library(dplyr)
library ("ISLR")
library (glmnet)
library(gglasso)
library(stringr)
library(combinat)
library(parallel)
library(MASS)
library(future.apply)
library(Metrics) ## AUC function for categorical outcome variable
```

# Laptop Dataset
```{r}
df <- read.csv("laptops.csv")

df$Inches <- ifelse(df$Inches == 11.3 | df$Inches == 11.6, 11, df$Inches)
df$Inches <- ifelse(df$Inches == 12 | df$Inches == 12.5 | df$Inches == 12.3, 11, df$Inches)
df$Inches <- ifelse(df$Inches == 13.3 | df$Inches == 13.9 | df$Inches == 13.5, 13, df$Inches)
df$Inches <- ifelse(df$Inches == 14.1, 13, df$Inches)
df$Inches <- ifelse(df$Inches == 15.4 | df$Inches == 15.6, 15, df$Inches)
df$Inches <- ifelse(df$Inches == 17 | df$Inches == 17.3, 15, df$Inches)
df <- df[df$Inches != 10.1 & df$Inches != 18.4, ]

df$Weight <- str_extract(df$Weight, "\\d\\.?+\\d?")
df$Weight <- as.numeric(df$Weight)

reordered_levels <- levels(df$Memory)[order(table(df$Memory))]
df$Memory_reordered <- factor(df$Memory, levels = reordered_levels)
df$Memory_reordered <- droplevels(factor(df$Memory, levels = reordered_levels))

df$Inches <- as.factor(df$Inches)
reordered_levels <- levels(df$Inches)[order(table(df$Inches))]
df$Inches <- factor(df$Inches, levels = reordered_levels)

df$Ram <- as.factor(df$Ram)
reordered_levels <- levels(df$Ram)[order(table(df$Ram))]
df$Ram <- factor(df$Ram, levels = reordered_levels)

df$OpSys <- as.factor(df$OpSys)
levels(df$OpSys) <- c("Others", "Others", "Linux", "Linux", "Linux", "Others", "Windows", "Windows", "Windows")
reordered_levels <- levels(df$OpSys)[order(table(df$OpSys))]
df$OpSys <- factor(df$OpSys, levels = reordered_levels)

df$TypeName <- as.factor(df$TypeName)
reordered_levels <- levels(df$TypeName)[order(table(df$TypeName))]
df$TypeName <- factor(df$TypeName, levels = reordered_levels)

df$Company <- as.factor(df$Company)
reordered_levels <- levels(df$Company)[order(table(df$Company))]
df$Company <- factor(df$Company, levels = reordered_levels)
```

```{r}
training_prop <- 0.6
n_observ <- dim(df)[1]
size <-  training_prop * n_observ
samp <- sort(sample(seq(n_observ), size =size))
train_df <- df[samp,]
test_df <- df[-samp,]
```

#################################
## Input:
### train_df ### 
### cols_tobeCoded ###
### other_predictors = NULL ###
### y_col ###
### seed = 99999 ###
### standardize = FALSE ###
### intercept = TRUE ###
#################################

## Case 1: Normal
```{r}
cols_tobeCoded = c("OpSys", "Inches")
other_predictors = c("Weight")
y_col = c("Price_euros")
seed <- 99999
standardize <- FALSE
intercept <- TRUE
```

```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("OpSys", "Inches"), 
                                 other_predictors = c("Weight"), 
                                 y_col = c("Price_euros"))
```
```{r}
testing(test_df, result_from_training)
```

## Case 2: No other predictors

```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("OpSys", "Inches"), 
                                 other_predictors = NULL, 
                                 y_col = c("Price_euros"))
```

```{r}
testing(test_df, result_from_training)
```

## Case 3: One predictor to be coded & Two other predictors

```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("OpSys"), 
                                 other_predictors = c("Inches", "Weight"),
                                 y_col =  c("Price_euros"))
```

```{r}
testing(test_df, result_from_training)
```

## Case 4: Change Default Parameters
```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("OpSys"), 
                                 other_predictors = c("Inches", "Weight"),
                                 y_col =  c("Price_euros"),
                                 seed = 999,
                                 standardize = TRUE,
                                 intercept = TRUE)
```

```{r}
testing(test_df, result_from_training)
```

# Wage Dataset

## Case 1: Normal 
```{r}
wage_data <- Wage
```

```{r}
training_prop <- 0.6
n_observ <- dim(wage_data)[1]
size <-  training_prop * n_observ
samp <- sort(sample(seq(n_observ), size = size))
train_df <- wage_data[samp,]
test_df <- wage_data[-samp,]
```

## Case 1: Normal
```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("maritl"), 
                                 other_predictors = c("age"),
                                 y_col =  c("wage"),
                                 seed = 999,
                                 standardize = TRUE,
                                 intercept = TRUE)
```

```{r}
testing(test_df, result_from_training)
```

## Case 2: Two factors to be Coded
```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("maritl", "race"), 
                                 other_predictors = c("age"),
                                 y_col =  c("wage"),
                                 seed = 999,
                                 standardize = TRUE,
                                 intercept = TRUE)
```

```{r}
testing(test_df, result_from_training)
```

## Case 3: Categorical Outcome Variables 
```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("maritl"), 
                                 other_predictors = c("age"),
                                 y_col =  c("race"),
                                 seed = 999,
                                 standardize = TRUE,
                                 intercept = TRUE,
                                 fit_family = "multinomial")
```

```{r}
testing(test_df, result_from_training)
```

# Aussies Dataset

```{r}
df <- read.csv("aussies.csv")
```

```{r}
df$LBM <- ifelse(df$LBM <= 60, 60, df$LBM)
df$LBM <- ifelse(df$LBM > 60 & df$LBM <= 70, 70, df$LBM)
df$LBM <- ifelse(df$LBM > 70 & df$LBM <= 80, 80, df$LBM)
df$LBM <- ifelse(df$LBM > 80, 90, df$LBM)
df$LBM <- factor(df$LBM)

df <- df[(df$SportN != 3) & (df$SportN != 8) & (df$SportN != 9), ]
#df$SportN <- ifelse(df$SportN > 60 & df$SportN <= 70, 70, df$SportN)
df$SportN <- factor(df$SportN)
```


```{r}
training_prop <- 0.8
n_observ <- dim(df)[1]
size <-  training_prop * n_observ
samp <- sort(sample(seq(n_observ), size = size))
train_df <- df[samp,]
test_df <- df[-samp,]
```


## Case 1: Normal
```{r}
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("LBM"), 
                                 other_predictors = c("Ht", "Wt"),
                                 y_col =  c("RCC"),
                                 seed = 999,
                                 standardize = TRUE,
                                 intercept = TRUE)
```

```{r}
testing(test_df, result_from_training)
```

## Case 2: Categorial Outcome Variable 
### (training dataset should have enough instances within each categorical outcome)

```{r}
source("function_0822.R")
result_from_training <- training(train_df = train_df, 
                                 cols_tobeCoded = c("LBM"), 
                                 other_predictors = c("Ht", "Wt", "RCC", "WCC"),
                                 y_col =  c("SportN"),
                                 seed = 999,
                                 standardize = TRUE,
                                 intercept = TRUE)
```

```{r}
testing(test_df, result_from_training)
```